---
title: "02_generate_tfl.Rmd"
output: html_document
---

Load in necessary libraries 
```{r}

library(DBI)
library(RSQLite)
library(gtsummary)
library(here)
library(reticulate)
library(officer)
library(flextable)

``` 

In order to load in the config file, which has the file paths listed for artifact (tables listings and figures) output, we need to setup a python virtual environment 

In the terminal run (only need to run once when setting up R session):
`uv venv -p 3.11` 

In the R console (only need to run once when setting up R session)
`reticulate::use_virtualenv("./.venv")`

Continue setting up reticulate and load in config variables 
```{r}

config = import_from_path(module = "config", path = here("source", "notebooks", "helpers"))
output_file_path = config$OUTPUT_ARTIFACT_PATH

```

Load in data from python step 
```{r}

conn = dbConnect(RSQLite::SQLite(), "sample.sqlite")

patients = dbGetQuery(conn, "SELECT * FROM filtered_patients")

```

Create output table using tbl_summary 
```{r}
output_table = patients |>
  select(AGE, GENDER, RACE, ETHNICITY, IS_SMOKER, HOSPITALIZATION_COUNT) |>
  tbl_summary() |>
  #convert to flex table for officer output 
  as_flex_table()

```

Use officer to create output word file 
```{r}

output_title = 'Table 1. Patient characteristics'

output_doc = read_docx() |>
  body_add(output_title) |>
  body_add_flextable(output_table) 

print(output_doc, file.path(output_file_path, 'patient_characteristics_tables.docx'))

```
